% =============================================================================
% PROJECTS
% =============================================================================
\newcommand{\cloudscale}{
\textcolor{color3}{\textbf{CloudScale — Distributed Microservices Platform}:}
\begin{itemize}
\item Designed and deployed a \href{https://github.com/johndoe/cloudscale}{microservices platform} handling 1M+ daily requests with 99.9\% uptime on AWS.
\item Emphasized scalability and maintainability through clean architecture and containerized services.
\end{itemize}
}

\newcommand{\codeinsight}{
\textcolor{color3}{\textbf{CodeInsight — AI Code Review Assistant}:}
\begin{itemize}
\item Built an \href{https://github.com/johndoe/codeinsight}{AI-powered tool} reducing code review time by 40\% across 10+ engineering teams.
\item Focused on developer experience with intuitive feedback and seamless GitHub integration.
\end{itemize}
}

\newcommand{\datastream}{
\textcolor{color3}{\textbf{DataStream — Real-time Analytics Pipeline}:}
\begin{itemize}
\item Developed a \href{https://github.com/johndoe/datastream}{stream processing system} ingesting 500K+ events per minute using Kafka and Spark.
\item Prioritized fault tolerance and low-latency insights for business-critical dashboards.
\end{itemize}
}

\newcommand{\devtrack}{
\textcolor{color3}{\textbf{DevTrack — Developer Productivity Dashboard}:}
\begin{itemize}
\item Created an \href{https://github.com/johndoe/devtrack}{internal analytics tool} used by 200+ developers to track performance and delivery metrics.
\item Delivered actionable insights through clean UI design and meaningful data visualization.
\end{itemize}
}

