\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvcolor{blue}
\moderncvstyle{contemporary}




% To compile through VS code. Basic input for document template and letter variations
\input{loader/preamble.tex}
\input{loader/variants_cv.tex}  



% Observe that the TEXINPUTS commands MUST be changed in setting.json (when shift + cmd + P) if the folder arrangement changes (i.e. this template or any other goes inside a folder in the same dir as cls/ or loader/)

\newcommand{\rolename}{asdf}   % To refer to your current job pos
\newcommand{\skills}{Skill 1, Skill 2} % To be modified when modular.

\newgeometry{top=0.5cm,
             left=2cm,
             right=2cm,
             bottom=1.8cm}  % Slim top



\name{John}{Doe} % Needs to be changed with some init
\email{johndoe@gmail.com}
\social[whatsapp]{+123456789}
\social[linkedin]{johndoe}
\social[github]{JohnDoe}
%\photo[1pt][0pt]{}

\newcommand{\projectone}{\cloudscale}
\newcommand{\projecttwo}{\devtrack}
\newcommand{\projectthree}{\datastream}

\begin{document}

\makecvtitle

\vspace{-0.0cm}



\section{Technical Skills \& Competencies}
\begin{itemize}

\item \textbf{Programming Languages:} Python, Java, TypeScript, C++, SQL

\item \textbf{Backend Development:} RESTful APIs, GraphQL, Microservices Architecture, API Design

\item \textbf{Frontend Development:} React, HTML5, CSS3, JavaScript (ES6+)

\item \textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Kubernetes, CI/CD (GitHub Actions)

\item \textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis

\item \textbf{Tools \& Practices:} Git, Linux, Unit \& Integration Testing, Agile/Scrum, System Design, Code Review

\item \textbf{Software Engineering:} Scalable System Design, Performance Optimization, Clean Code, Design Patterns

\item \textbf{Languages:} English (C2), Japanese (N3)


\section{Projects}
\begin{itemize}
\item \projectone
\item \projecttwo
\item \projectthree
\end{itemize}

\end{itemize}

\vspace{0.2cm}



\section{Work Experience}
\cventry{2021--2026}{\textcolor{color3}{Senior Software Engineer}}{TechNova Inc.}{Tokyo, Japan}{}{
\begin{itemize}
\item Led development of scalable backend services supporting 500K+ users globally.
\item Improved system performance by 35\% through optimization and architectural redesign.
\item Mentored junior developers and introduced CI/CD pipelines reducing deployment time by 50\%.
\end{itemize}
}

\cventry{2018--2021}{\textcolor{color3}{Software Engineer}}{CodeWorks Ltd.}{Remote}{}{
\begin{itemize}
\item Built RESTful APIs and frontend features for SaaS applications used by 50K+ users.
\item Collaborated in Agile teams to deliver high-quality software on tight deadlines.
\end{itemize}
}

\section{Education}
\cventry{2018--2020}{\textcolor{color3}{M.Sc. in Computer Science}}{University of Edinburgh}{Edinburgh, UK}{}{}

\cventry{2014--2018}{\textcolor{color3}{B.Sc. in Computer Science}}{University of Technology}{London, UK}{}{}
\end{document}